---
title: "Homework 1"
author: Allison Stewart
output: github_document 
---

This is my solution for HW1. 

```{r}
library(tidyverse)
```


## Problem 1 

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10), 
    samp_gt_0 = samp > 0, 
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"), 
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame. 

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r try_numeric_multiply}
as.numeric(pull(prob1_df, samp_gt_0)) * (pull(prob1_df, samp))
as.factor(pull(prob1_df, samp_gt_0)) * (pull(prob1_df, samp))
```


## Problem 2 

```{r load_palmerpenguins}
data("penguins", package = "palmerpenguins")
```

**Description of Penguins dataset**

This dataset includes the variables: `r variable.names(penguins)`. 

The size of the dataset is `r nrow(penguins)` rows by `r ncol(penguins)` columns. 

The mean flipper length is `r summarize(penguins, mean(flipper_length_mm, na.rm=T))`. 

Make a scatterplot of flipper length vs bill length. 

```{r scatterplot}
ggplot(data=penguins, aes (x = bill_length_mm, y = flipper_length_mm)) + geom_point(aes(color = species)) + scale_color_manual(values = c("red", "green", "blue"))
ggsave("penguins.jpeg")
```

This scatterplot plots flipper length vs bill length and distinguishes the species by color. 

